---
title: "Account Report"
output: html_document
---

Account report for Handelsbanken account. Data formatting might have to be modified if used for different accounts/banks.

# Overall Development

The overall development shows changes of the account's assets over time since the start of the account.

## Account Balance

The account balance is the most popular metric and shows simply the level of cash in the account.

```{r, echo=FALSE, message=FALSE}
if(!require(ggplot2)){
  install.packages('ggplot2')
  require(ggplot2)
}
library(scales)
source('helpers.R')

datafile <- 'kontotransactionlist.csv'

data <- read.delim( datafile )
data <- sanetizedata(data)


g.balance <- ggplot( data=data, aes(x=Date, y=Balance), color="green")
g.balance <- g.balance + ylab("Balance k SEK") + xlab("Transaction Date")
g.balance <- g.balance + geom_line(colour = 'green3') + geom_smooth(colour='black') + scale_y_continuous(labels=comma)
print(g.balance)
```

## Transfer Volume

The transfer volume graph lets easily spot peaks in volume transfers, i.e. when large chunks have been moved around

```{r, echo=FALSE}
col.sign <- c('red3','green3')
col.bar <- col.sign[(sign(data$Amount)+1)/2+1]
g.volume <- ggplot( data=data, aes(Date, abs(Amount))) + ylab("Volume")
g.volume <- g.volume + ylab("Volume k SEK") + xlab("Transaction Date")
g.volume <- g.volume + geom_bar(colour=col.bar, stat = "identity") + scale_y_continuous(labels=comma)

print(g.volume)
```

# Monthly Analysis

Here we will add a `for-loop` that goes through all months and visualizes certain assets of the account
